
\RequirePackage{amsmath}
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage[utf8]{inputenc} \usepackage[T1]{fontenc} 
\usepackage{url}
\usepackage{hyperref}
\usepackage{color}
\usepackage{soul}
%\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{a4wide}
\usepackage{amsmath}
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
 \renewcommand\UrlFont{\color{blue}\rmfamily}
%\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\red}[1]{#1}

\begin{document}
%
\title{Optimal Solutions to Common Interview Problems}
\subtitle{A Summary of Chapter II.Problems of the EPI book}

\author{Sarah Lutteropp}

\authorrunning{S. Lutteropp}

\maketitle

\begin{abstract}

In this document, I summarize the main optimal solution approaches for common coding interview problems. This document is meant for personal use. (And for making my handwritten notes easier to read \ldots)

\end{abstract}

\section{Interview Toolbox}

\subsection{Primitive Types / Bit Tricks}

\paragraph{Remove lowest set bit in $x$}
$$x = x \& (x-1)$$

\paragraph{Isolate lowest set bit in $x$}
$$x \& ~(x-1)$$

\paragraph{Extract i-th bit of $x$}
$$x \& (1 << i)$$

\paragraph{Swap bits}
Only needed if the bits are not the same. If needed, it's like flipping bits:
$$x \wedge = ((1 << i) | (1 << j))$$

\paragraph{Reverse bits}
Use precomputed lookup table for 16-bit words.
If $x = y_1 y_2 y_3 y_4$, then $\text{rev}(x) = \text{rev}(y_4) \text{rev}(y_3) \text{rev}(y_2) \text{rev}(y_1) $.
Useful for this: $0xFFFF = 65535 = 2^{16}-1 = 1111.1111.1111.1111$ (16 ones)

\paragraph{Closest integer with same number of ones}
If we flip bits at index $i$ and $j$, the absolute difference is $|2^i - 2^j|$.
Thus, we need to swap the two rightmost consecutive bits that differ.

\paragraph{$x*y$ without arithmetic operations}
Add using bitwise operations. Multiply using shift-and-add (grade-school) algorithm.

\paragraph{$x/y$ using only +, -, and bitshifts}
Idea: Find largest $k$ such that $2^k * y \leq x$, substract $2^k$ fom $x$, and add $2^k$ to the quotient.

\paragraph{Compute $x^y$}
If $y$ is negative, replace $x$ by $1/x$ and $y$ by $-y$.
Idea: $(x^\frac{y}{2})^2$ or $x * (x^\frac{y}{2})^2$

\paragraph{Check if decimal is palindrome}
A negative number can't be palindromic.

\begin{itemize}
	\item Number of digits in integer $x$:
$$n = \lfloor \log_10(x) \rfloor + 1$$

	\item Least significant (last) digit in integer $x$:
$$x \mod 10$$

	\item Most significant digit in integer $x$:
$$\frac{x}{10^{(\lfloor \log_10 x \rfloor + 1)}}$$

	\item Remove most significant digit:
$$x = x \mod 10^{\text{num\_digits - 1}}$$

	\item Remove least significant digit:
$$x = x / 10$$
\end{itemize}

\paragraph{Generate uniform random numbers in range $[a,b]$ given random 0/1 values}
Same as in range $[0, b-a]$.

Easy if $[b-a] = 2^i - 1$ for some $i$: Generate each bit of a $i$-bit number.

Otherwise, search smallest $i$ such that $2^i - 1 \geq b - a$, and redo generation if out of range.


\paragraph{Rectangle intersection (parallel to x- and y-axis)}
Focus on when rectangles \textbf{don't} intersect, handle x- and y-dimension separately.

\subsection{Arrays}
\subsection{Linked Lists}
\subsection{Stacks}
\subsection{Queues}
\subsection{Binary Trees}
\subsection{Heaps}
\subsection{Searching}
\subsection{Hash Tables}
\subsection{Sorting}
\subsection{Binary Search Trees}
\subsection{Recursion}
\subsection{Dynamic Programming}
\subsection{Greedy Algorithms}
\subsection{Invariants}
\subsection{Graphs}

\section{Cool C++ features}

\section{Cool Python Features}

% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
 \bibliographystyle{splncs04}
 \bibliography{document}


\end{document}
